\texorpdfstring{Identifying Software Performance Changes Across\\ Variants and Versions}{Identifying Software Performance Changes Across Variants and Versions}

### 2020-08-31 paper.tex
ran aspell spell check and fixed minor typos

		We have conducted a number of experiments both on controlled synthetic datasets as well as in real-world scenarios with different software systems. Our evaluation demonstrates that we can pinpoint performance shifts to individual configuration options and interactions as well as commits introducing change points with high accuracy and at scale. Experiments on three real-world systems explore the effectiveness and practicality of our approach.

@@

	For our DBMS example, we present a fully determined performance-influence model in Equation~\ref{eq:pimodel_dbms}. The first two terms correspond to the features \textsc{Encrpytion} and \textsc{Compression}, respectively. The third term respresents the interaction of both features. The configuration parameter $c_{\textsc{Compr}\land\textsc{Encrypt}}$ evaluates to $1$, if both $c_{\textsc{Encrypt}}$ and $c_{\textsc{Compr}}$ evaluate to $1$.
	That is, $c_{\textsc{Compr}\land\textsc{Encrypt}} \equiv c_{\textsc{Encrypt}} \cdot c_{\textsc{Compr}}$. In the last term, we omit the configuration parameter $c_\emptyset$, as this term represents invariable functionality.

	\begin{align} \label{eq:pimodel_dbms}
	\begin{split}
	\Pi_{\text{DBMS}}(c) =&~\beta_{\textsc{Encrpyt}} \cdot c_{\textsc{Encrpyt}} + \beta_{\textsc{Compr}} \cdot c_{\textsc{Compr}} \\
	+&~ \beta_{\textsc{Compr\ $\land$\ Encrpyt}} \cdot c_{\textsc{Compr\ $\land$\ Encrpyt}}
	+ \beta_{\emptyset}
	\end{split}
	\end{align}

@@

	As each iteration yields a candidate solution, we keep track of associations in a \emph{solution cache} and repeatedly update the confidence of associations. 
	The rationale is not to lose previously identified change points, but at the same time, allow for removing identified changes points that are likely false positives due to new measurements.
	Some associations, especially in the beginning, might be influenced by sampling bias and can be removed if successive iterations do not repeatedly revisit these associations. 
	The algorithm terminates if the solution cache does not change for a number of iterations or a maximum number of iterations/measurements has been reached.
	In what follo, we present the steps of our approach in detail.

@@

	All measurements were conducted on clusters of Ubuntu machines with Intel~Core
	2 Quad CPUs (2.83~GHz) and 8~GB of RAM (\textsc{xz} and \textsc{lrzip}) and 16~GB of RAM (\textsc{oggenc}). To mitgate measurement bias, we repeated each measurement five times. The coefficient of variation (the ratio of standard deviation and the arithmetic mean) across all machines was well below ten percent. For commits that did not build, we reported the performance measurement of the most recent commit that did not fail to build.

@@

	In Figure~\ref{fig:results_rq1_degree}, we decompose the reported F1 scores to learn how the number of change points or the interaction degree influence our approach. The x-axis shows the highest interaction degree of change points for an experiment run. For interactions of a degree up to 5, the F1 score is mostly above 0.5. We observe a downward trend in the boxplots: the more change points a system contained, the less accurate our algorithm's prediction is.

>>>>

		We have conducted a number of experiments both on controlled synthetic data sets as well as in real-world scenarios with different software systems. Our evaluation demonstrates that we can pinpoint performance shifts to individual configuration options and interactions as well as commits introducing change points with high accuracy and at scale. Experiments on three real-world systems explore the effectiveness and practicality of our approach.

@@

	For our DBMS example, we present a fully determined performance-influence model in Equation~\ref{eq:pimodel_dbms}. The first two terms correspond to the features \textsc{Encryption} and \textsc{Compression}, respectively. The third term represents the interaction of both features. The configuration parameter $c_{\textsc{Compr}\land\textsc{Encrypt}}$ evaluates to $1$, if both $c_{\textsc{Encrypt}}$ and $c_{\textsc{Compr}}$ evaluate to $1$.
	That is, $c_{\textsc{Compr}\land\textsc{Encrypt}} \equiv c_{\textsc{Encrypt}} \cdot c_{\textsc{Compr}}$. In the last term, we omit the configuration parameter $c_\emptyset$, as this term represents invariable functionality.

	\begin{align} \label{eq:pimodel_dbms}
	\begin{split}
	\Pi_{\text{DBMS}}(c) =&~\beta_{\textsc{Encrypt}} \cdot c_{\textsc{Encrypt}} + \beta_{\textsc{Compr}} \cdot c_{\textsc{Compr}} \\
	+&~ \beta_{\textsc{Compr\ $\land$\ Encrypt}} \cdot c_{\textsc{Compr\ $\land$\ Encrypt}}
	+ \beta_{\emptyset}
	\end{split}
	\end{align}

@@

	As each iteration yields a candidate solution, we keep track of associations in a \emph{solution cache} and repeatedly update the confidence of associations. 
	The rationale is not to lose previously identified change points, but at the same time, allow for removing identified changes points that are likely false positives due to new measurements.
	Some associations, especially in the beginning, might be influenced by sampling bias and can be removed if successive iterations do not repeatedly revisit these associations. 
	The algorithm terminates if the solution cache does not change for a number of iterations or a maximum number of iterations/measurements has been reached.
	In what follows, we present the steps of our approach in detail.

@@

	All measurements were conducted on clusters of Ubuntu machines with Intel~Core
	2 Quad CPUs (2.83~GHz) and 8~GB of RAM (\textsc{xz} and \textsc{lrzip}) and 16~GB of RAM (\textsc{oggenc}). To mitigate measurement bias, we repeated each measurement five times. The coefficient of variation (the ratio of standard deviation and the arithmetic mean) across all machines was well below ten percent. For commits that did not build, we reported the performance measurement of the most recent commit that did not fail to build.

@@

	In Figure~\ref{fig:results_rq1_degree}, we decompose the reported F1 scores to learn how the number of change points or the interaction degree influence our approach. The x-axis shows the highest interaction degree of change points for an experiment run. For interactions of a degree up to 5, the F1 score is mostly above 0.5. We observe a downward trend in the box plots: the more change points a system contained, the less accurate our algorithm's prediction is.
